%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode


\documentclass[11pt]{article}

\usepackage{xunicode}
\usepackage{xltxtra}

\usepackage[english]{babel}

% Document layout.
\usepackage{geometry}
	\geometry{letterpaper,
	          textwidth=6.3in,
	          textheight=9in,
	          marginparsep=7pt,
	          marginparwidth=.6in,
	          right=1in}
	\setlength\parindent{0in}

% Fonts.
\usepackage{fontspec}
% Converts LaTeX specials (``quotes'', --- dashes, etc.) to Unicode.
\defaultfontfeatures{Mapping=tex-text}
	\setromanfont[Ligatures=Common,Numbers=OldStyle]{Adobe Caslon Pro}
	\setmonofont[Scale=0.8]{Monaco}
	\setsansfont[Scale=0.9]{OptimaLTStd}

\newfontfamily\FAR{Font Awesome 5 Free Regular}
\newfontfamily\FAS{Font Awesome 5 Free Solid}
\newfontfamily\FAB{Font Awesome 5 Brands Regular}

% Custom ampersand.
\newcommand{\amper}
           {{\fontspec[Scale=.95]
                      {Adobe Caslon Pro}\selectfont\itshape\&}}

% Symbols.
\def\symPhone{\FAS \symbol{"F879}}  % Phone
\def\symEmail{\FAR \symbol{"F2B6}}  % Email
\def\symGithub{\FAB \symbol{"F09B}}  % GitHub

% Margin years.
\usepackage{marginnote}
	\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
	\renewcommand*{\raggedleftmarginnote}{}
	\setlength{\marginparsep}{7pt}
	\reversemarginpar

% Headings.
\usepackage{sectsty}
\usepackage[normalem]{ulem}
	\sectionfont{\rmfamily\mdseries\Large}
	\subsectionfont{\rmfamily\mdseries\scshape\normalsize}
	\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize}

% PDF setup.
\usepackage[dvipsnames]{xcolor}
\usepackage[xetex,
            unicode,
            bookmarks,
            colorlinks,
            breaklinks,
            pdftitle={Víctor Manuel Muñoz Berti -- cv},
            pdfauthor={Víctor Muñoz}]
           {hyperref}
\hypersetup{linkcolor=NavyBlue,
            citecolor=NavyBlue,
            filecolor=black,
            urlcolor=NavyBlue}


\begin{document}

\begin{minipage}[m]{.3\textwidth}
	{\LARGE Víctor Muñoz}
\end{minipage}
\begin{minipage}[m]{.45\textwidth}
	346A South Lambeth Road, Flat 11.\\
	London SW8 1UQ.
\end{minipage}
\begin{minipage}[m]{.25\textwidth}
	{\symPhone} \texttt{+44 7913 308666}\\
	{\symEmail} \href{mailto:victorm@marshland.es}{victorm@marshland.es}
	{\symGithub} \href{https://github.com/bolsote}{github.com/bolsote}
\end{minipage}\\[.05cm]


\section*{Experience}  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent

\years{2018--2021}\textsc{Senior Software Developer}, \href{https://sohonet.com}{Sohonet}, London, UK.

Member of the product development team of a leading service provider for the media and entertainment industry. We were tasked with providing software to movie studios and production companies.

Responsibilities and specific projects:
\begin{itemize}
	\item  FileRunner 2: Maintenance of our legacy file transfer application.\\
	\textit{Technologies}: OpenStack Swift, Python, Django, MySQL, Celery, JavaScript, jQuery.
	\item  FileRunner 3: Design and development of our next generation file transfer application. The main objective was to create a fast upload experience, by leveraging parallelism both at the browser and the infrastructure levels. This enabled the transfer of multi--terabyte files, as is characteristic of the media industry. Performed management duties for the frontend sub--team.\\
	\textit{Technologies}: OpenStack Swift, Python, SQLAlchemy, Marshmallow, Nameko, PostgreSQL.
	\item  {ClearView Flex}: Design and development of our industry--leading video streaming platform. The main objective was to build a ultra--low latency streaming solution, built on commodity hardware and standard network connections. This allowed members of the media industry to share and get feedback on anything from live editing sessions to live camera footage. Involvement in all three sub--teams: backend, frontend, and systems.\\
	\textit{Technologies}: Python, SQLAlchemy, Marshmallow, Nameko, PostgreSQL, Redis, ElasticSearch, JavaScript, React, Redux, C, gstreamer, ffmpeg, Puppet, Terraform, Linux, Docker, Packer.\\
	\textit{Awards}:
	\begin{itemize}
		\item 2020 HPA Engineering Excellence Awards Honourable Mention.
		\item 2020 Engineering Emmy® Award.
	\end{itemize}
\end{itemize}

\years{2017--2018}\textsc{CTO}, \href{http://loncom.com}{LonCom}, London, UK.

We continued the work started in Shared Property Data under the umbrella of LonRes, an established company in the PropTech sector.

Responsibilites and specific projects:
\begin{itemize}
	\item  As the lead architect I designed a new system from the ground up, learning from our experience running Shared Property Data. The result was a system much more stable and straightforward than its predecessor, which allowed us to build a much more connected and coherent property graph.
	\item  Design and development of a transactional engine capable of creating a property graph, linking commercial property lettings and sales, agents, firms, and properties.\\
	\textit{Technologies}: Python, SQLAlchemy, Marshmallow, PostgreSQL, ElasticSearch.
	\item  Design and development of a REST API around the core engine.\\
	\textit{Technologies}: Pyramid, Gunicorn.
	\item  Coordinated the development of a web frontend, consuming the APIs and providing a user-friendly experience, tailored around the needs of commercial property agents and built based on their direct feedback.\\
	\textit{Technologies}: TypeScript, React, Redux.
	\item  Coordinated the devops aspect, ensuring the team got exact requirements for both development and production systems, and collaborating closely with them during the process.\\
	\textit{Technologies}: Ansible, Docker, Linux.
	\item  As a tech lead I coordinated a team of between four and six people, managing the technical architecture and collaborating with our product owner in the creation of a product roadmap.
	\item  As a board member I took part in shaping the general business strategy, and liaising with stakeholders to align the technical and commercial visions.
\end{itemize}

\years{2014--2017}\textsc{Lead Software Engineer/CTO}, \href{http://myspd.co.uk}{Shared Property Data}, London, UK.

Responsibilities and specific projects:
\begin{itemize}
	\item  First technical member of the team; architected, prototyped and wrote the product, and led its evolution.
	\item  Design and development of a REST API, acting as the backend for the whole platform.\\
	\textit{Technologies:} Python, Django REST Framework, PostgreSQL, Celery.
	\item  Unit, integration, regression, penetration, performance and acceptance test suites; automated QA through a CI system.\\
	\textit{Technologies:} Pytest, Jasmine, Karma, Jenkins.
	\item  Development of a consumer--facing frontend, based on a modern, single--page application. It serves as a reference implementation for an API consumer.\\
	\textit{Technologies:} JavaScript, AngularJS 1.x.
	\item  Design and evolution of a semantic, fine--grained and geospatial search engine. \\
	\textit{Technologies:} Apache Solr, ElasticSearch.
	\item  Systems administration, including staging and production servers, as well as management of the deployment process.\\
	\textit{Technologies:} FreeBSD, Nginx, Salt.
\end{itemize}

\years{2014}\textsc{Software Engineer}, \href{http://www.wazoku.com}{Wazoku}, London, UK.

Responsibilities and specific projects:
\begin{itemize}
	\item  Senior backend engineer, in charge of maintaining the company's product (Idea Spotlight), and planning, implementing, testing and deploying new features.\\
	\textit{Technologies:} Python, Django, Bottle, JavaScript, CouchDB, PostgreSQL, ElasticSearch, Celery.
	\item  Implementation of a brand--new search engine, based on Apache Solr, aimed at improving the reliability and performance of the previous system, as well as extending the search capabilities of the application, providing room for future improvements and extensions.\\
	\textit{Technologies:} Apache Solr, Haystack.
	\item  Creation of a new configuration management and deployment system, aimed at increasing the system's reliability, scalability and fault tolerance, while reducing downtime during the deployment of new versions of our application.\\
	\textit{Technologies:} Fabric, Salt, Grunt, HAProxy.
	\item  Acting systems administrator, responsible for monitoring the company's cloud infrastructure and solving any incidence in the shortest time possible, thus maintaining our SLA.\\
	\textit{Technologies:} Linux, Nginx, Monit, Python.
	\item  Maintenance of the test suite, running it through a continuous integration system and verifying its build status before every release, guaranteeing that every release is clean.\\
	\textit{Technologies:} Nose, Jenkins.
\end{itemize}

\years{2011--2013}\textsc{Lead developer}, \href{http://www.iteisa.com}{ITEISA Desarrollo y Sistemas, S.L.}, Santander, Spain.

General tasks:
\begin{itemize}
	\item  Management of the software development process and code life cycle, from requirements analysis and specification to deployment and maintenance.
	\item  Level 3 technical support, performing tasks regarding performance and security code audits, software installation, upgrading and configuration and end--user training.\\
	\textit{Technologies:} OTRS.
	\item  Implementation of the ISO/IEC 15504 standard; preparation of the documentation regarding software development process and testing methodologies.
	\item  Streamlining of the company's software development process, migrating to a version control system, an issue tracking platform and an automated configuration and deployment system.\\
	\textit{Technologies:} Git, GitLab, Puppet.
\end{itemize}

Specific projects:
\begin{itemize}
	\item  Design and development of a search engine on top of the whole body of parliamentary acts of the Spanish Congress; performance and accuracy testing and tuning.\\
	\textit{Technologies:} Apache Solr, Kyoto Cabinet, OpenNLP, OpenCalais, Perl.
	\item  Design an development of a window configuration system, to be integrated into a window manufacturer website.\\
	\textit{Technologies:} JavaScript, Processing.js, jQuery, CakePHP, MySQL.
	\item  Design, development and deployment of a real--time distributed rendering system for a shoe--customisation web application; strong focus on integration, performance and system testing.\\
	\textit{Technologies:} CakePHP, ImageMagick, MySQL, FastCGI, POV--Ray, Autodesk Maya, ZeroMQ.
	\item  Design and development of a scraper to extract the gas price for all gas stations in Spain from the official database; development of web and mobile apps, using custom algorithms to improve search results based on user's history and localisation.\\
	\textit{Technologies:} Python, Requests, SQLAlchemy, MySQL, CakePHP, HTML5, jQuery Mobile, PhoneGap.
\end{itemize}

\years{2011}\textsc{HW/SW engineer}, \href{http://www.tedesys.com}{TEDESYS Global, S.L.}, Santander, Spain.
\begin{itemize}
	\item  Design and implementation of a stereo vision system; adapting current computer vision algorithms for implementation in a FPGA system.\\
	\textit{Technologies:} C/C++, VHDL, OpenCV, dc1394, Boost.
\end{itemize}

\years{2008,2009}Summer grant, \href{http://www.imm.cnm.csic.es/magnetoplasmonics}{Magnetoplasmonics group}, Madrid Microelectronics Institute (IMM -- CSIC), Madrid, Spain.
\begin{itemize}
	\item  Debugging, improving and extending a scattering--matrix based numerical code, to be executed in a multi--processor system.\\
	\textit{Technologies:} C/C++, BLAS, Lapack.
\end{itemize}


\section*{Education} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
\years{2005--2010}\textsc{MSc} in Telecommunications Engineering, Universidad de Cantabria; speciality on microelectronics.

\subsection*{Microelectronics specialisation}
\noindent
Design and verification of digital integrated circuits.\\
Design of full--custom analog integrated circuits.\\
Embedded systems design, especially systems on chip (SoC). Development of task--specific hardware accelerators in VHDL.


\section*{Languages} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
\textsc{Spanish}, native speaker.\\
\textsc{English}, fluent. Technical assessment in juridic and technical translations.


\section*{IT Skills} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Programming languages}
\noindent
Python, JavaScript, TypeScript, UNIX shell scripting.\\
Working knowledge of C, C++, Ada, PHP and Go.

\subsection*{Operating system administration}
\noindent
Linux, *BSD (OpenBSD, FreeBSD).

\subsection*{Web development}
\noindent
\textsc{Frontend:} HTML5 \amper{} CSS3, JavaScript, React, Redux.\\
\textsc{Backend:} MVC frameworks based on Python (Django, Flask, Bottle) and on PHP (CakePHP).

\subsection*{Database management systems}
\noindent
\textsc{Relational databases:} MySQL, PostgreSQL.\\
\textsc{NoSQL databases:} MongoDB, Redis, CouchDB.\\
\textsc{Search engines:} Apache Solr, Elastic Search.

\subsection*{Version control systems}
\noindent
\textsc{Centralised:} Subversion.\\
\textsc{Distributed:} Git.


\end{document}
